Environmental stress affects niche breadth in plant-pollinator communities

### 2019-11-30 paper/manuscript.Rmd
Sensitivity analysis figure back to the main text for thesis

After performing our sensitivity analysis, we found that we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
We, therefore, removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
When inspecting the suitability values of the analysed species, we found that most communities included species for which habitat suitability was low and species for which it was high (Fig. \@ref(fig:fig-median-suitability)).

>>>>

After performing our sensitivity analysis, we found that we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
We, therefore, removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
When inspecting the suitability values of the analysed species, we found that most communities included species for which habitat suitability was low and species for which it was high (Fig. \@ref(fig:fig-median-suitability)).
```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
loadd(sensitivity_species_name)
fig_sensitivity_analysis_legend <- 
  paste0("Sensitivity analysis of environmental stress error. ",
         "The number of independent occurrences retrieved from GBIF is inversely related to the error of bioclimatic suitability for our plant-pollinator networks.", 
         "The sensitivity analysis was performed by subsampling occurrences of", 
         " *", sensitivity_species_name$canonicalName, "* ", 
         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")

readd(fig_sensitivity_analysis)
```

### 2019-11-30 paper/supp-info.Rmd
Move world map to supplementary info
Sensitivity analysis figure back to the main text for thesis

@@

```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}

fig_sensitivity_analysis_legend <- 
  paste0("Sensitivity analysis of environmental suitability error. ",
         "The number of independent occurrences retrieved from GBIF is inversely related to the error of environmental suitability for our plant-pollinator networks.", 
         "The sensitivity analysis was performed by subsampling occurrences of", 
         " *", sensitivity_species_name$canonicalName, "* ", 
         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")

readd(fig_sensitivity_analysis)
```

>>>>

```{r fig-worldmap, fig.width = width('single'), fig.cap ="Worldwide distribution of pollination communities included in this study"}
readd(fig_worldmap)
```

@@
